---
title: "Class Demo document"
author: "Kyle Thayer"
format: html
---

## Trying out some formatting

Let's see if I can make text **Bold**

How about *italics*

If I write text here and make it **Bold**, *Italics*, or ***both***, I can see how to do it.

### Test some lists

An unordered list of ingredients:

-   flour
-   butter
-   sugar
    -   Note: this will be brown sugar
-   etc.

An ordered list

1.  melt butter
2.  mix ingredients
3.  bake

## Code examples

First I am going to save some values in variables

```{r}
num_students_201 <- 198
num_openings_201 <- 200

open_slots <- num_openings_201 - num_students_201
```

I am teaching INFO 201. There are currently `r num_students_201` students registered out of `r num_openings_201` open spots for the class. That means, `r open_slots` more students could sign up.


## Example of code with National Park dataset
Step 1: Load National Park data and Dplyr
```{r}
#| warnings: hidden
#| messages: hidden

library(dplyr)

# Load a dataset of the top 5 national parks by visits

np_top_5_df <- read.csv("https://raw.githubusercontent.com/melaniewalsh/Neat-Datasets/refs/heads/main/2020-National-Park-Visits-By-State-Top5.csv")

```

Step 2: Get values from the dataset
```{r}

# Note: Pipe takes the results from before and makes them the first argument of the next function
# eg. np_top_5_df |> nrow()
#   is the same as nrow(np_top_5_df)
# or np_top_5_df |> pull(RecreationVisits)
#   is the same as pull(np_top_5_df, RecreationVisits)

# number of parks in my dataset
num_parks <- nrow(np_top_5_df)

total_visits <- np_top_5_df |>
                pull(RecreationVisits) |>
                sum()

avg_visits <- np_top_5_df |>
              pull(RecreationVisits) |>
              mean() |>
              round()

```

We looked at the top `r num_parks` National Parks. Those parks had a total of `r total_visits` different visits. And those parks together had an average of `r avg_visits` visits.
