---
title: "Demo quarto doc saving"
author: "Kyle Thayer"
format:
  html:
    embed-resources: true
---

Load libraries: (Note: I think I finally got this to not show the extra messages when loading the libraries!)
```{r}
#| warning: false

# load dplyr and ggplot2 library
library("dplyr")
library("ggplot2")
```

Load dataset and find some averages:

```{r}
fake_student_df <- read.csv("https://raw.githubusercontent.com/kylethayer/Info-201-au-24-datasets/refs/heads/main/demo_L03_fake_students.csv")


# multistep pipe to find averages
avg_student_num <- 
  fake_student_df |> 
    pull(student_num) |> 
    mean()

avg_student_final <- 
  fake_student_df |> 
    pull(final_exam_score) |> 
    mean(na.rm = TRUE)

avg_student_final_with_0s <- mean(72, 93, 87, 0, 54)

```

The average student number is `r avg_student_num`. The average final exam score (for students who showed up) was `r avg_student_final`. But the final exam score if I count students who didn't show up as getting 0s is `r avg_student_final_with_0s`.

## Example graph:
```{r}


midwest <- midwest

#scatter plot of points with x/y axis based on college degrees
# and poverty
ggplot(data = midwest) +
  geom_point(mapping = aes(x = percollege, y = percadultpoverty))

```

