---
title: "Lecture 9: review demo"
format: html
---

## Try doing filter and summarize on a dataframe
load dplyr and get pocket dataframe
```{r}
library(dplyr)
library(stringr)
pocket_df <- read.csv("https://github.com/the-pudding/data/raw/master/pockets/measurements.csv")
```

Now try to filter for all pants that have polyester, and then find the average price. Method 1: not using summarize
```{r}
avg_price_polyester <- 
  pocket_df |>
  filter(str_detect(fabric, "polyester")) |>
  pull(price) |>
  mean()
```

Example paragraph here. The average price of all pants with polyester is $`r round(avg_price_polyester)`.

If I wanted to purchase one of each of the non-polyester pants, how much would it cost? Method 2: use summarize
```{r}
total_non_polyester_price <-   
  pocket_df |>
  filter(!str_detect(fabric, "polyester")) |>
  summarize(total_cost = sum(price)) |>
  pull(total_cost) # This gets the total_cost out of a dataframe
```
(Note: there are data issues where polyester is sometimes abbreviated as "poly")

I can't display directly a dataframe with multiple values (sometimes made by summarize). Total cost of all non-polyester pants (rounded) is $`r total_non_polyester_price`.

